\chapter*{Abstract}
This thesis primarily considers evolved exoplanetary systems through the use of asteroseismology as an analysis tool to investigate the fundamental properties of the host stars, and the inferred parameters of  planets orbiting them. Of particular interest are the masses of evolved stars, and investigating how the available observables may bias the recovered mass estimates. Accurate and precise stellar masses are of critical importance when investigating the occurrence rates of planets. Whilst most of this work considers ensemble analysis, where applicable individual systems are considered in detail, including a binary star system with an M dwarf orbiting an asteroseismic red giant primary star. Another system of note is a transiting gas giant orbiting a red giant primary that will be consumed by the expansion of the host star on an astronomically short timescale. Along with the masses of evolved stars, the metallicity distributions of evolved exoplanet hosts, and a suitable ensemble of field stars are investigated using spectroscopy. This is to determine if evolved giant planet exoplanet hosts display the same metallicity excess seen in main sequence giant planet hosts. We fail to find a statistically significant excess in metallicity. Finally the noise properties of evolved stars are considered, how the noise properties of the star can be predicted from stellar parameters, and the impact that elevated noise levels in evolved stars impact the detectable of planets around them. 

\thispagestyle{plain}

%  Ack
\chapter*{Acknowledgements}
This thesis would not have been completed without the help and support of many people in my life. Firstly, my parents, sister, and grandparents who have spent the last 20 years or so listening to me talk about space and planets all the time. Without their help and encouragement I would never have gotten here. Secondly, to my officemates and all members of HiROS, but particularly James and Caitlin for helping me fix code and drink wine. Thirdly, to my supervisor Bill Chaplin for putting up with me for another 4 years after supervising my Masters project. Fourthly, my  girlfriend Beth, for tolerating my moaning about thesis writing whilst you were writing your thesis also. Finally, a special mention should be made to Taylors coffee for sustaining me through the many long hours of writing and editing this thesis\footnote{see \cite{writerblock}}.
\thispagestyle{plain}