\chapter*{Acknowledgements}
\thispagestyle{plain}

Firstly, I would like to sincerely thank my supervisor, Professor Bill Chaplin. Thank you for inspiring me to enjoy solar and stellar physics as a undergraduate, for your advice and support throughout this Ph.D., and also for allowing me the freedom to explore other creative ventures during my studies.

I would also like to thank my secondary supervisor, Professor Cristina Lazzeroni, for expert support during my Ph.D. and offering me opportunities to get involved in outreach and engagement activities.

I would also like to thank Dr. Angela Romano and Dr. Francesco Gonnella for their valuable support. In addition, thank you to Dr. Steve Hale for advice and for allowing me aid on a maintenance visit to Carnarvon. My experience was made much easier with their guidance.

Thanks to all colleagues within and connected to the Solar and Stellar Physics (SASP) group, or Sun, Stars, and Exoplanets (SSE) group, and within the Astrophysics and Space Research (ASR) group. I would particularly like to thank my incredible fellow Ph.D. students: Vedad, Tom, Ben, Mat, Oli, Alex D., Saniya, Matt, Walter, George, Emma, Alex L., Lindsey, and Emily, for some fantastic memories. The games, drinks, meals out, tea breaks, and friendship all made my experience absolutely delightful. Furthermore, thank you to the postdocs: Ted, Martin, Warrick, Matteo, Jake, and Elinore.

This Ph.D. would not have been possible without the work of the staff in the School of Physics and Astronomy and the wider support staff at the University of Birmingham. Thank you namely to Kat Grover, Lou Barden, Maria Pavlidou, and Holly Prescott; in addition to the staff in the Physics and Astronomy stores and the education support office.

Thank you to my family for supporting me through the Ph.D.: Mum, Dad, Hayley, Chris, and Connor. Thank you to all my friends, new and old, who have been a part of this with me. An enormous thank you to Dr. Hannah Serrage whose enthusiasm, kindness, and wisdom has helped me tremendously through this odyssey.

Finally, thank you to my reviewers and editors, and my thesis committee.