\chapter*{Structure of Thesis}\label{chap:struct}
\textit{Text on how thesis is structured. Also a statement of what work you did yourself.}%Delete this line

This thesis is comprised of four analysis chapters in addition to an introduction and conclusion. These chapters cover five separate projects I have completed during my PhD. At the start of each chapter a detailed statement is given explaining the contribution of work by myself or collaborators for each project. 

Chapters \ref{chap:reta} and \ref{chap:noise} have already been published (\citealt{2017North_reta} and \citealt{2017North} respectively), where I am first author on both works. These chapters are reproductions of the published works, aside from minor formatting changes to comply with thesis regulations. 

Chapter \ref{chap:evolvedhosts} is comprised of two separate works that share many analysis techniques. Both halves of the chapter are presented in a format commensurate with the structure of a paper. Two papers are in preparation and will be submitted soon. I shall be first and second author on these papers respectively.

Finally, Chapter \ref{chap:spec} is also presented in a format similar to a paper, and is essentially a draft near to submission, that again I shall be first author on. 

As some of the chapters are verbatim reproductions of published or works in preparation, there is a level of repetition between some of the introductory and analysis sections, in each chapter, and Chapter \ref{chap:intro}. 
 